### 2024-06-16 research-methods.qmd
20240615 - clarification

Inter-rater reliability evaluates the consistency of scores across raters.
For instance, if we have a strong measure for assessing college players' aptitude to succeed in the NFL, the measure should yield a similar score for a given player regardless of which (trained) rater (e.g., coach) uses it to rate the player.
The consistency of scores across raters is commonly evaluated using the intraclass correlation coefficient (for continuous variables) and Cohen's kappa ($\kappa$; for categorical variables).

@@

Intra-rater reliability evaluates the consistency of scores within a given rater.
If we have a strong measure for assessing college players' aptitude to succeed in the NFL, the measure should yield a similar score for a given player from the same (trained) rater (e.g., coach) each time they rate the same player.
The consistency of scores within raters can be evaluated using similar approaches as those evaluating [inter-rater reliability](#sec-interraterReliability).

@@

Reliability and validity are different but related.
Reliability refers to the *consistency* of scores, whereas accuracy refers to the *accuracy* of scores.
Validity depends on reliability.
Reliability is necessary—but insufficient for—validity.
That is, consistency is necessary—but insufficient for—accuracy.
As depicted in @fig-reliabilityVsValidity, a measure can be no more valid than it is reliable.

>>>>

Inter-rater reliability evaluates the consistency of scores across raters.
For instance, if we have a strong measure for assessing college players' aptitude to succeed in the NFL, the measure should yield a similar score for a given player regardless of which (trained) rater (e.g., coach or talent scout) uses it to rate the player.
The consistency of scores across raters is commonly evaluated using the intraclass correlation coefficient (for continuous variables) and Cohen's kappa ($\kappa$; for categorical variables).

@@

Intra-rater reliability evaluates the consistency of scores within a given rater.
If we have a strong measure for assessing college players' aptitude to succeed in the NFL, the measure should yield a similar score for a given player from the same (trained) rater (e.g., coach or talent scout) each time they rate the same player (assuming the player's aptitude has not changed).
The consistency of scores within raters can be evaluated using similar approaches as those evaluating [inter-rater reliability](#sec-interraterReliability).

@@

Reliability and validity are different but related.
Reliability refers to the *consistency* of scores, whereas accuracy refers to the *accuracy* of scores.
Validity depends on reliability.
Reliability is necessary—but insufficient for—validity.
That is, consistency is necessary—but insufficient for—accuracy.
As depicted in @fig-reliabilityVsValidity, a measure can be no more valid than it is reliable.
A measure can be consistent but inaccurate; however, a measure cannot be accurate but inconsistent.
